StarCraft Bots and Competitions

### 2015-12-16 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
Very small change in SSCAIT section intro.

\subsection{SSCAIT}\label{sec:SSCAIT}
The Student StarCraft AI Tournament\footnote{\url{http://sscaitournament.com/}} (SSCAIT) started in 2011 at Comenius University in Bratislava, Slovakia and has been well known for being the Starcraft AI competition with the highest number of total participants. Started as a part of a course in artificial intellignece at Comenius University, each SSCAI tourament includes several dozen student submissions from this course in addition to submissions from across the globe. 
There are three fundamental differences between SSCAIT and the remaining two conferences:
\begin{enumerate}
  \item SSCAIT is an online-only event. Unlike AIIDE or CIG, it is not co-located with a scientific conference or any other real-world event.
  \item There are two phases of SSCAIT each year: a {\em competitive} phase, lasting for up to three weeks and a {\em sandbox} phase which runs for approximately eleven months each year. In other words, SSCAIT is live at all times with only a few short interruptions.
  \item All the games are publicly {\em streamed live} 24 hours a day. The stream uses a custom observer script \cite{mattsson2015automatic} designed specifically to improve the viewer experience and creates a continuous feedback loop for the participants who can watch their bots play against the others.
\end{enumerate}

>>>>

\subsection{SSCAIT}\label{sec:SSCAIT}
The Student StarCraft AI Tournament\footnote{\url{http://sscaitournament.com/}} (SSCAIT) started in 2011 at Comenius University in Bratislava, Slovakia and has been well known for being the Starcraft AI competition with the highest number of total participants. Started as a part of a course in artificial intellignece at Comenius University, initial SSCAIT seasons included several dozen student submissions from this course in addition to submissions from across the globe. 
There are three fundamental differences between SSCAIT and the remaining two conferences:
\begin{enumerate}
  \item SSCAIT is an online-only event. Unlike AIIDE or CIG, it is not co-located with a scientific conference or any other real-world event.
  \item There are two phases of SSCAIT each year: a {\em competitive} phase, lasting for up to three weeks and a {\em sandbox} phase which runs for approximately eleven months each year. In other words, SSCAIT is live at all times with only a few short interruptions.
  \item All the games are publicly {\em streamed live} 24 hours a day. The stream uses a custom observer script \cite{mattsson2015automatic} designed specifically to improve the viewer experience and creates a continuous feedback loop for the participants who can watch their bots play against the others.
\end{enumerate}
